---
title: "Reproducible Research: Peer Assessment 1"
author: "MALLESH SUBRAMANI M"
date: "18 August 2018"
output: html_document
---
## Loading and preprocessing the data
In the following code we try to load the required packages,read the data from the csv file and clean the data
```{r, echo=TRUE}
setwd("~/github/RepData_PeerAssessment1")
#setwd("~/git/RepData_PeerAssessment1")
library(lubridate)
activity <- read.csv("activity.csv")
activity$date <- ymd(activity$date)
activity <- activity[!is.na(activity$steps), ]
```

## What is mean total number of steps taken per day?
We use tapply function to find the sum of the steps with respect to the date and then use a histogram plot to plot the data

```{r 1,echo=TRUE}
act_sum <- tapply(activity$steps,activity$date,sum)
hist(act_sum
     ,col = "black"
     ,breaks = 20
     ,xlab = "steps"
     ,ylab = "freq"
     ,main = "histogram of number of steps")
median(activity$interval)     #finding the median 
mean(activity$interval)       #finding the mean

```


## What is the average daily activity pattern?
Finding the average of steps with respect to the interval and creating a time series plot
```{r 2,echo=TRUE}
steps <- tapply(activity$steps,activity$interval,mean)
steps1 <- data.frame(step=steps,interval=as.numeric(names(steps)))
rownames(steps1) <- (1:length(steps1$step))
plot(steps1$step~steps1$interval
     ,type="l"
     ,col="red"
     ,xlab="interval"
     ,ylab="steps")
```

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
